<NAME> - an analyser framework for P4

### 2021-03-22 publications/The_tool_intro/paper.tex
tool_intro:some motivation

	\begin{abstract}
		TODO
	\end{abstract}

@@

  \subsection{Compiler} % 1 hasáb - Dániel
  In related research~\cite{cscs18,ocs20}, we work on a static cost analysis tool for P4: the tool expects as input a P4 program source code together with execution environment parameters, and outputs various metrics (e.g. execution time, energy efficiency) without actually running the P4 program.

>>>>

	\begin{abstract}
		There are many important tasks in a conventional software development process which can be supported by different analysis techniques. P4 is a high level domain specific language for
describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts often make analysis of P4 programs a laborious task. 
The paper presents <NAME>, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way. The framework uses an integral graph representation which contains the results of applied analysis methods too. This way the framework supports rapid implementation of new analysis methods in a way where the results will be also easily reusable by other methods.

	\end{abstract}

@@

  \subsection{Compiler} % 1 hasáb - Dániel
  In related research~\cite{cscs18,LukacsOcs}, we work on a static cost analysis tool for P4: the tool expects as input a P4 program source code together with execution environment parameters, and outputs various metrics (e.g. execution time, energy efficiency) without actually running the P4 program.
